%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
%\usepackage[hidelinks]{hyperref}
\usepackage[colorlinks,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage{geometry}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\geometry{left=0.2in,top=0.2in,right=0.2in,bottom=0.2in}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Yanjie He} 
	& Phone: (202)733-7796 \\
	LinkedIn: \url{https://www.linkedin.com/in/yanjiehe/}
	& Email : \href{mailto:heyanjie0@outlook.com}{heyanjie0@outlook.com} \\
	Github: \url{https://github.com/YanjieHe}
	& Portfolio of Projects: \url{https://yanjiehe.github.io/} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The George Washington University}{Washington D.C., USA}
      {Master of Science in Data Analytics (Computer Science Track)}{Anticipated May. 2020}
    \resumeSubheading
      {Shanghai University of International Business and Economics}{Shanghai, China}
      {Bachelor of Arts in Economics;  GPA: 3.71/4.00}{Sept. 2013 -- June. 2017}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skils}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{: C++, C\#, Java, Scala, Python, R, SQL, Scheme/Racket, HTML/CSS/JavaScript}
    \resumeSubItem{Modeling Skills}{: Machine Learning, Statistics, Social Network Analysis, Natural Language Processing}
    \resumeSubItem{Database}{: MySQL, SQL Server, Sqlite3}
    \resumeSubItem{Frameworks \& Libraries}{: Qt5, React.js, D3.js, Spark, Eigen, OpenCV}
    \resumeSubItem{Tools \& Technologies}{: Linux, Gephi, Recommender System, Compiler Design}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Machine Learning Researcher}{Oct 2018 - Anticipated Feb 2019}
      {George Washington University}{Washington D.C. Metro Area, USA}
      \resumeItemListStart
        \resumeItem{Project Title}{Artificial Intelligence and User Behavior for Robust Near Real-Time Recommendations}
        \resumeItem{Position}
        {Group research collaborator for Dr. Benjamin Harvey, faculty of the George Washington University}
 	    \resumeItem{Recommender System}
 	    {Designing a graph-based recommender system, utilizing collected user behaviors data. }
	    \resumeItem{Software Development}
	    {Developing the recommender system using C++, Java, and Python. Implementing machine learning algorithms to build robust models. Using Github for collaborative development and version control. Utilizing Restful Api to provide interoperability between front-end and back-end. }
        \resumeItem{Information Retrieval}
        {Applying methods in Natural Language Processing to explore information from user activities in the browser. }
      \resumeItemListEnd

    \resumeSubheading
      {Computational Social Scientist}{Sep 2018 - Anticipated Apr 2019}
      {George Washington University}{Washington D.C. Metro Area, USA}
      \resumeItemListStart
	  \resumeItem{Social Network Analysis and Data Analysis}
	  { Working with Professor Vontrese Pamphile at the George Washington University, applying mathematical and statistical techniques to novel data.  }
	  \resumeItem{Analytical Programming}
	  { Reviewing academic papers. Using Python and R to clean the dataset and run the models. Applying D3.js to visualize data.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Jul 2016 - Feb 2017}
      {Kantar Media CIC}{Shanghai, China}
      \resumeItemListStart
 	  \resumeItem{Data Collection}
 	  {Collected online comments with team members utilizing Python, and provided data cleaning solution using C\# and SQL Server for Chanel APAC project.}
	  \resumeItem{Data Visualization}
	  {Developed Data Visualization Solution in C\# for GroupM television show, to plot Venn Graph according to given data automatically.}
 	  \resumeItem{Text Mining System}
	  { Developed a text mining system in C\# with team members. The system was used by more than 50 data analysts in the company to make data analysis solution for L'Oréal, Chanel, Volkswagen, and Dell. Saved more than 10,000 dollars of outsourcing cost. The system was processing millions of text data records every month. }
  	  \resumeItem{Sentiment Analysis}
      {
  	  	Improved the accuracy of sentiment analysis by 17\% compared to the previous tool used in the company.
  	  	\begin{enumerate}
  	  		\item Used jieba package in Python to cut the Chinese sentences into separated words.
  	  		\item Selected words as features that are important for classification by $\chi^2$ test.
  	  		\item Applied the logistic regression to classify the sentiment of user comments.
  	  	\end{enumerate}
      }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{A Compiler and a Virtual Machine}
    {
        Developed a compiler for a statically typed language, a bytecode disassembler, and a virtual machine in C++.
    }
    \resumeSubItem{A Content-based Movie Recommender System}
    {
        Developed a content-based movie recommnder system in C++ and Python. Extracted information of colors and audio from movie trailers, and utilized the network relationship between movies. Applied Collaborative Topic Regression to solve the cold-start problem.
    }
    \resumeSubItem{Text Co-occurrence Network Analysis for The Hunger Games}
    {
	    Completed a text analysis project where implemented text co-occurrence network to visualize the relationship between the main characters in the novel \textit{The Hunger Games}. Written the program in Python and used packages including nltk, pandas, matplotlib and wordcloud. Plotted the network by using Gephi.
    }
  \resumeSubHeadingListEnd


%    \resumeSubItem{Reversi A.I.}
%    {
%      Reversi is a board game. Due to the huge amount of possible states of the game, it is next to impossible for a computer to enumerate every situation. Therefore, I implemented the minimax algorithm with alpha-beta pruning. The project is written in C++ and has a GUI which is build using Qt5 Framework.
%    }
%    \resumeSubItem{Compiler and Virtual Machine}
%      {
%        Developed a compiler for a statically typed language, a bytecode disassembler, and a virtual machine.
%        And also, designed a bytecode instruction list, which is similar to the JVM instructions. Wrote the compiler and disassembler in \textbf{C++}, and the virtual machine in ANSI C.
%      }
%    \resumeSubItem{Landscape Image Clustering based on Color Histogram}
%    {
%	Completed a computer vision project. 
%	\begin{itemize}
%	  \item Wrote a web crawler to download the landscape images from the Internet.
%	  \item Used C++ to extract color histogram as image features based on OpenCV framework
%      \item Finally run the K-Means model on Apache Spark using scala to cluster the data.
%	\end{itemize}
%    }

\end{document}
